Analysis of celiac disease

### 2017-12-13 5-results-celiac.Rmd
save

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%", 
                      fig.asp = 0.7, error = TRUE)
options(width = 85)
```

@@

```{r}
# Read file, see "Preprocessing" notebook
celiac <- snp_attach("backingfiles/celiacQC.rds")
G <- celiac$genotypes
CHR <- celiac$map$chromosome
POS <- celiac$map$physical.pos
NCORES <- nb_cores()
y <- celiac$fam$affection - 1
```

@@

```{r}
labels <- 1:22; labels[c(11, 13, 15, 17, 18, 20, 21)] <- ""
cowplot::plot_grid(
  snp_manhattan(gwas.train.gc, CHR, POS, labels = labels),
  snp_manhattan(gwas.train.gc, CHR, POS, labels = labels) +
    coord_cartesian(ylim = c(0, 30)) + 
    geom_hline(yintercept = -log10(5e-8), color = "red", linetype = 3),
  align = "hv", ncol = 1, labels = LETTERS[1:2], label_size = 25, scale = 0.95
)
```

```{r}
ggsave("figures/celiac-man.png", scale = 1/90, width = 1400, height = 1000)
```

@@

Cross-Model Selection and Averaging:

@@

```{r}
ggsave("figures/celiac-regpath.pdf", scale = 1/90, width = 1000, height = 700)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%", fig.width = 10,
                      fig.asp = 0.7, dev = "svg")
options(width = 95)
```

@@

```{r}
# Read file, see "Preprocessing" notebook
library(bigsnpr)
celiac <- snp_attach("backingfiles/celiacQC.rds")
G <- celiac$genotypes
CHR <- celiac$map$chromosome
POS <- celiac$map$physical.pos
NCORES <- nb_cores()
y <- celiac$fam$affection - 1
```

@@

```{r, dev="png"}
labels <- 1:22; labels[c(11, 13, 15, 17, 18, 20, 21)] <- ""
cowplot::plot_grid(
  snp_manhattan(gwas.train.gc, CHR, POS, labels = labels),
  snp_manhattan(gwas.train.gc, CHR, POS, labels = labels) +
    coord_cartesian(ylim = c(0, 25)) + 
    geom_hline(yintercept = -log10(5e-8), color = "red", linetype = 3),
  align = "hv", ncol = 1, labels = LETTERS[1:2], label_size = 25, scale = 0.95
)
```

```{r}
ggsave("figures/supp-celiac-man.png", scale = 1/90, width = 1300, height = 1000)
```

@@

Cross-Model Selection and Averaging (CMSA):

@@

```{r}
ggsave("figures/main-celiac-regpath.pdf", scale = 1/90, width = 1000, height = 700)
```
